---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/mdsumner/sctrip.svg?branch=master)](https://travis-ci.org/mdsumner/sctrip)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdsumner/sctrip?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/sctrip)

# sctrip

The goal of sctrip is to reboot the trip package on a firmer basis. 

It's not very functional yet, but the goal is to create normal-form PATH objects that fit within a very general 
framework for structured data. PATHs aren't that useful in normal-form, but converting from external path-forms to PRIMITIVE forms and back is **very useful**.  More soon. 

## Installation

You can install sctrip from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdsumner/sctrip")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sctrip)
apath <- sc_path(aurora, LONGITUDE_DEGEAST, LATITUDE_DEGNORTH, DATE_TIME_UTC)
```

The PATH object can be converted to PRIMITIVE form: 

```{r primitive}
sc::PRIMITIVE(apath)
```

We can do that no matter what choice we made when nominating the vertex columns. 

```{r flexible}
sc::PRIMITIVE(sc_path(aurora, DATE_TIME_UTC, LATITUDE_DEGNORTH))
```
